%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience (9+ years)}


%------------------------------------------------~-------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
  {Senior Fullstack Developer} % Job title
  {DOMINO'S} % Organization~
  {Istanbul, Turkey} % Location
  {09 / 2023 - ... (1 year 4 months)}
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed the SuperApp CMS application from scratch, a back-office application for new businesses.}
      \item {Developed the backend of a superapp application hosting multiple brands using Node.js, JavaScript, and AWS. The mobile version of one of the brands is available here: \href{https://play.google.com/store/apps/details?id=com.trcoffy.live&hl=en}{\textbf{Coffy}}.}
      \item {Created documentation and diagrams about the project and CI / CD Pipeline.}
      \item {\textbf {Skills:} React.js · TypeScript · Redux.js · Vite · Material UI · Bitbucket Pipeline · Node.js · Javascript · AWS · NewRelic}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Senior Full Stack Developer, Tech Lead} % Job title
    {GETIR} % Organization~
    {Istanbul, Turkey} % Location
    {01 / 2020 - 09 / 2023 (3 years 8 months)}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Getir is a technology company that provides q-commerce to its customers in grocery delivery business (available in 9 countries). Additionally, Getir has some other services in Turkey like food delivery, taxi, car rental, jobs, e-commerce.}
        \item {Witnessed the growth of my organization from 500 members to ~30000 members (12 billion{\$} value) in just ~4 years, and deeply involved in solving the problems it brought.}
        \item {Migrated Getir's core admin application from angular1.x to React structure.}
        \item {Developed a user authorization structure which allows user roles, permission levels, permission request, page or component based access.}
        \item {Developed {\&} Maintained web application of Getir's core business (grocery product delivery).}
        \item {Set up initial unit testing structure for our react admin application.}
        \item {Proactively participated in technical refinement sessions in system designs.}
        \item {Onboarding, supporting and training new team members at both a junior and senior level.}
        \item {Migrated monolith service to micro-services.}
        \item {Developed new features on web application of Getir's food delivery business.}
        \item {Wrote technical documents for all projects that we completed.}
        \item {\textbf {Skills:} React.js · Javascript · Redux.js · Node.js · MongoDB}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {AKINON} % Organization
    {Istanbul, Turkey} % Location
    {09 / 2018 - 01 / 2020 (1 year 4 months)}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Akinon is a cloud-based headless commerce platform.}
        \item {Built a configurable e-commerce mobile application using React Native and Expo, enabling us to create over 20 iOS and Android applications with different designs and capabilities.}
        \item {Played a vital role in integrating tools into the React Native app, including Google Analytics, Sentry, push notification integrations, revenue tracking, event tracking, product recommendations, deep linking, and crash reporting.}
        \item {Developed a Mobile Application Builder platform that allows internal users to configure mobile applications, modify design and functionalities, and deploy apps onto development or production environments.}
        \item {Developed a deployment pipeline using Jenkins to deploy mobile apps onto test or live platforms.}
        \item {\textbf {Skills:} React.js · Javascript · React Native · Node.js · MongoDB}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {CODTRA} % Organization
    {Istanbul, Turkey} % Location
    {07 / 2017 - 08 / 2018 (1 year 1 month)}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Codtra is a chatbot company that offers chatbot solutions for social platforms like facebook, twitter, skype, etc.}
        \item {Developed chatbot applications for facebook messenger and skype.}
        \item {Developed several web applications.}
        \item {Built a payment integration system with Stripe.}
        \item {Developed an image generator package that combines image and text(s) with given positions.}
        \item {Published an image manipulation package on azure to be able to run imagemagick library on azure.}
        \item {\textbf {Skills:} Javascript · AngularJS · Facebook API · Node.js · MongoDB}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {FEDERAL SMART} % Organization
    {Istanbul, Turkey} % Location
    {02 / 2016 - 06 / 2017 (1 year 4 months)}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Federal Smart Solutions Inc. is an IOT company that have projects using IOT, bluetooth, BLE, beacon, RFID technologies.}
        \item {Built web and Android-based IoT applications.}
        \item {Developed an admin application for "Pick 'n' Watch," which shows a promotional video when a customer touches the product, using BLE, Beacon, AngularJS, and native Android technologies.}
        \item {\textbf {\textbf {Skills:}} Javascript · AngularJS}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
