%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%------------------------------------------------~-------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {Expense Tracker GraphQL App} % Project Title
    {Personal Project} % Company
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an expense tracker application using the MERN stack with Apollo GraphQL.}
        \item {Implemented type definitions, resolvers, and mutations for managing and modifying data.}
        \item {Integrated authentication with Passport.js and managed global state with Apollo Client.}
        \item {\textbf {Skills:} MongoDB · Express.js · React.js · Node.js · Apollo GraphQL · Passport.js · Render · Tailwind CSS}
      \end{cvitems}
    }

    \cventry
    {Full Stack Developer} % Job title
    {Trend League - trendligi.com} % Project Title
    {Personal Project} % Company
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a website that displays the top trending posts from various social media platforms including Twitter, YouTube, Reddit, and 9GAG.}
        \item {Implemented web scraping using Puppeteer to crawl social media sites on a country basis and list the most trending posts.}
        \item {Ensured data was constantly updated by running scraping jobs every two hours, which involved sorting data based on specific criteria and generating a list of the top 50 most popular posts.}
        \item {Addressed challenges related to logging in as a user, bypassing captchas, avoiding rate limiting errors, and using different IP addresses for scraping.}
        \item {\textbf {Skills:} React.js · Redux · Node.js · MongoDB · AWS · Puppeteer · Web Scraping · Cron Jobs}
      \end{cvitems}
    }

  \cventry
    {Frontend Developer} % Job title
    {Villa Rental Website} % Project Title
    {Freelance Project} % Company
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed to the development of a villa rental website by adding new features.}
        \item {Worked on the front-end using React, Redux, and Next.js.}
        \item {\textbf {Skills:} React.js · Redux · Next.js · TypeScript}
      \end{cvitems}
    }

  \cventry
    {Full Stack Developer} % Job title
    {Getir Administration Panel (GAP)} % Project Title
    {@GETIR} % Company
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {GAP is a huge web application used in GetirHQ.}
        \item {All operations for Getir's market delivery business are carried out via GAP. For example, product creation, order refund actions, real-time monitoring for all assets, dashboarding and data visualizations.}
        \item {Led the project to convert from AngularJS to ReactJS from scratch.}
        \item {Implemented the front-end, back-end and microservices.}
        \item {Implemented page / component based user authorization structure.}
        \item {\textbf {Skills:} JavaScript · TypeScript · Node.js · MongoDB · NoSQL · Mongoose · AWS · S3 · React.js · Redux · Webpack}
      \end{cvitems}
    }

  \cventry
    {Full Stack Developer} % Job title
    {Restaurant Administration Panel (RAP)} % Project Title
    {@GETIR} % Company
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {RAP is a web application used by restaurants for getirfood.}
        \item {I maintained the codebase and added new features.}
        \item {\textbf {Skills:} JavaScript · Node.js · Docker · AWS · S3 · React.js · Redux · Webpack}
      \end{cvitems}
    }

  \cventry
    {Front-End Developer} % Job title
    {Franchise Administration Panel (FAP)} % Project Title
    {@GETIR} % Company
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {FAP is a web application used by franchises for getir.}
        \item {I maintained the codebase and added new features.}
        \item {\textbf {Skills:} JavaScript · React.js · Redux · Webpack}
      \end{cvitems}
    }

  \cventry
    {Full Stack Developer} % Job title
    {ApplicationBuilderPlatform (ABP)} % Project Title
    {@AKINON} % Company
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Web-based platform to automate building applications with specified configurations.}
        \item {It is used for building EcommerceMobileApp (mobile) and Instore (web) applications.}
        \item {I took part in both back-end and front-end development.}
        \item {\textbf {Skills:} JavaScript · Node.js · MongoDB · NoSQL · Mongoose · AWS · S3 · React.js · Redux · Webpack}
      \end{cvitems}
    }

  \cventry
    {Full Stack Developer} % Job title
    {DeploymentPipeline} % Project Title
    {@AKINON} % Company
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {DeploymentPipeline is a jenkins pipeline to deploy specified app onto test or live platforms.}
        \item {It has some steps like cloning repo, downloading configurations, executing commands, deploying applications, etc.}
        \item {\textbf {Skills:} JavaScript · Node.js · Webpack · Jenkins}
      \end{cvitems}
    }

  \cventry
    {Mobile Application Developer} % Job title
    {EcommerceMobileApp} % Project Title
    {@AKINON} % Company
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {EcommerceMobileApp is a single-codebase, configurable, ecommerce react-native (mobile) application.}
        \item {I took responsibility for developing the core features of the application from scratch.}
        \item {I played a vital role in integrating third-party tools (platforms, services) like Google Analytics, Sentry, Insider, Segmentify, Commencis, and Visilabs, which provide analytics, push notifications, revenue tracking, event tracking, product recommendations, deep linking, and crash reporting.}
        \item {It has some steps like cloning repo, downloading configurations, executing commands, deploying applications, etc.}
        \item {\textbf {Skills:} JavaScript · React Native · Redux · Expo · Webpack · Jest · Mocha · Chai · Integration (Analytics, Push Notifications, Revenue Tracking, Event Tracking, Product Recommendations, Deep Links, Crash Reporting)}
      \end{cvitems}
    }

  \cventry
    {Front-end Developer} % Job title
    {Instore} % Project Title
    {@AKINON} % Company
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Instore is a single-codebase, configurable, ecommerce react (web) application. It is used in Akinon's customers' stores to sell products that are not available in-store but are available online. I developed and maintained the core features of this application.}
        \item {\textbf {Skills:} JavaScript · React.js · Redux · Webpack · Mocha · Chai · Jest}
      \end{cvitems}
    }

  \cventry
    {Full Stack Developer} % Job title
    {Domino Solutions} % Project Title
    {@CODTRA} % Company
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Web and Mobile-based application that enables corporate users to trigger and terminate business workflows over mobile devices.}
        \item {The platform is connected to some ERP and CRM software packages like SAP, EBA etc.}
        \item {Developed web app with angularjs and maintained back-end part by using dot-net.}
        \item {Implemented a stripe payment integration that allows to subscribe selected solutions monthly.}
        \item {\textbf {Skills:} JavaScript · React.js · Redux}
      \end{cvitems}
    }

  \cventry
    {Back-end Developer} % Job title
    {MigrosBot} % Project Title
    {@CODTRA} % Company
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Facebook Messenger Chatbot application for customers' use.}
        \item {Created the entire architecture includes network, security, database, API design, cache mechanism, performance, bot-ux-flow, etc.}
        \item {Implemented a dynamic image generator that composites product, price, text, font in a nice-looking way.}
        \item {Implemented a call center scenario with socket.io which allows customers to chat with the staffs via facebook messenger chatbot.}
        \item {Through this app, users can also see the nearest shops, authenticate with their phone number to join campaigns, and perform other cool tasks.}
        \item {\textbf {Skills:} JavaScript · Node.js · MongoDB · Redis · Socket.io · Facebook Messenger API · Azure}
      \end{cvitems}
    }

  \cventry
    {Android and Web Developer} % Job title
    {TowApp} % Project Title
    {@FEDERAL SMART} % Company
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Web and Android-based IOT project using BLE and Beacon technologies.}
        \item {The project is designed to warn users via SMS messages to prevent their cars from being towed.}
        \item {Developed an Android proximity tracker app that communicates with the server.}
        \item {Developed a web app to monitorize, manage and define app related stuffs.}
        \item {\textbf {Skills:} Android · Java · JavaScript · AngularJS · BLE · Beacon}
      \end{cvitems}
    }

  \cventry
    {Front-end Developer} % Job title
    {PickNWatch} % Project Title
    {@FEDERAL SMART} % Company
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Web and Android-based IOT project using BLE and beacon technologies.}
        \item {The project involves tracking the movement of a product using beacon sensors to play the related video on the screen.}
        \item {Developed the web app for PickNWatch to manage all operations.}
        \item {The project also includes role-based authentication, analytics, charts, dashboards, animations, google maps, interactive maps, inventory management, different language supports.}
        \item {\textbf {Skills:} JavaScript · AngularJS · BLE · Beacon}
      \end{cvitems}
    }

  \cventry
    {Full Stack Developer} % Job title
    {Akdeniz} % Project Title
    {@FEDERAL SMART} % Company
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Web and desktop-based warehouse management application using EPC GEN-2 RFID technology.}
        \item {Maintained codebase and developed new features.}
        \item {\textbf {Skills:} Csharp · .NET · RFID}
      \end{cvitems}
    }

  \cventry
    {Front-end Developer} % Job title
    {HgsPark} % Project Title
    {@FEDERAL SMART} % Company
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Web-based gate passing application using EPC GEN-2 RFID technology for cars and peoples.}
        \item {\textbf {Skills:} JavaScript · AngularJS · RFID}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
